Wavelet Spatio-Temporal Change Detection on multi-temporal SAR images

### 2021-11-03 tex/paper.wecs/wecs_tgrs.tex
Updates on application

We employed the proposed change detection method on a series of 85 multi-date satellite images. The images were taken on a forest region at the border of Brazil and the French Guiana from 2015-12-26 to 2017-12-3. Each image has two channels (VV and VH) and 1538 by 1556 pixels. We perform a change detection wavelet analyses on the combined image by considering each observed entry as $\mathcal{I}_{k,l}(m) = (\mathrm{VV}_{k,l}(m)^2+\mathrm{VH}_{k,l}(m)^2)^{1/2}$, where $\mathrm{VV}$ and $\mathrm{VH}$ represent the matrices of observations from VV and VH channels, respectively.

@@

\begin{figure}[htp!]
\includegraphics[scale=.13]{../../figs/forest_vSumDifCoefSq}\hspace{-.5cm}(a) 
\includegraphics[scale=.13]{../../figs/forest_wecs_abscorr}\hspace{-.5cm}(b)\\
\includegraphics[scale=.11]{../../figs/forest_wecs_change_space}\hspace{-.5cm}(c) 
\includegraphics[scale=.13]{../../figs/forest_aggreg_ratios}\hspace{-.5cm}(d)\\ 
\caption{Analysis of change points in time and space of the forest data. (a) Plot of $\vd(m)$, $m=1,\ldots,85$ with orange horizontal line indicating two times its median absolute deviation. (b) Matrix of absolute correlations obtained with WECS. (c) Change regions detected by highlighting the $[n/\log n]$ largest correlations. (d) Change measured with aggregation of absolute differences.}
\label{F:forest_wecs}
\end{figure}

>>>>

We employed the proposed change detection method on a series of 84 multi-date satellite images. The images were taken on a forest region at the border of Brazil and the French Guiana from 2015-12-26 to 2017-12-3. Each image has two channels (VV and VH) and 1538 by 1556 pixels. We perform a change detection wavelet analyses on the combined image by considering each observed entry as $\mathcal{I}_{k,l}(m) = (\mathrm{VV}_{k,l}(m)^2+\mathrm{VH}_{k,l}(m)^2)^{1/2}$, where $\mathrm{VV}$ and $\mathrm{VH}$ represent the matrices of observations from VV and VH channels, respectively.

@@

\begin{figure}[htp!]
\includegraphics[scale=.13]{../../figs/forest_vSumDifCoefSq}\hspace{-.5cm}(a) 
\includegraphics[scale=.14]{../../figs/forest_wecs_abscorr}\hspace{-.5cm}(b)\\
\includegraphics[scale=.10]{../../figs/forest_wecs_change_space}\hspace{-.5cm}(c) 
\includegraphics[scale=.14]{../../figs/forest_aggreg_ratios}\hspace{-.5cm}(d)\\ 
\caption{Analysis of change points in time and space of the forest data. (a) Plot of $\vd(m)$, $m=1,\ldots,85$ with orange horizontal line indicating two times its median absolute deviation. (b) Matrix of absolute correlations obtained with WECS. (c) Change regions detected by highlighting the $[n/\log n]$ largest correlations. (d) Change measured with aggregation of absolute differences.}
\label{F:forest_wecs}
\end{figure}
